% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number


\name{JINGWEN \(JESSICA\) WANG}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% {E-mail}{mobilephone}{homepage}
% be careful of _ in emaill address
\contactInfo{jingwen.w2010@gmail.com}{978-905-5985}{www.linkedin.com/in/jingwen-jessica-wang}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\faSearch\ Objective}
\datedsubsection{\textbf{Software Engineering Internship}}{Summer 2017}
\datedsubsection{\textbf{Data Science Internship}}{Summer 2017}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\faGraduationCap\ Education}

\datedsubsection{\textbf{University of Massachusetts Lowell}, MA. PhD, Computer Science, 3.8/4 GPA,}{expected May 2018}
%\textit{Ph.D. Candidate} in Computer Science, 3.8/4 GPA,

\datedsubsection{\textbf{University of Massachusetts Lowell}, MA. Master, Computer Science, 3.7/4 GPA,}{May 2013}
%\textit{Master} in Computer Science, 3.7/4 GPA

\datedsubsection{\textbf{Tianjin University of Science \& Technology}, China, B.S, Computer Science, 3.4/4 GPA,}{May 2010}
%\textit{B.S} in Computer Science, 3.4/4 GPA


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item \textbf{Programming Languages}: Java, Python, JavaScript, HTML, PHP
  \item \textbf{Tools}: MongoDB, MySQL, Git, Maven, Solr, Spring Boot, Yii, jQuery, Bootstrap
  \item \textbf{Experiences}: Information Extraction, Classification, Crawler, RESTful API, Full stack development
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\faUsers\ Projects}

%\datedsubsection{\textbf{University of Massachusetts} Lowell, MA}{2013 -- Present}
%\role{Research/Teaching Assistant}{}
%Research interests: machine learning, text modeling, and data mining, with a particular focus on
%applications applying these methods.


\datedsubsection{\textbf{Clinical Trials Data Modeling}}{May. 2016 -- Present}
\role{Java, Python, Solr, Django, Linux}{Research project}
A clinical trials knowledge discovering research project applying information retrieval, information extraction and data modeling methods.
\begin{itemize}
  \item Implemented big data real time search and analytics for over 12G of clinical trials data
  \item Developed conceptual search using word2vec method
\end{itemize}

\datedsubsection{\textbf{Kuaiwenbao News Feed System}}{May 2014 -- Aug. 2016}
\role{Full stack, Java, Python, PHP, JavaScript, jQuery, HTML}{Research project}
An automated online article crawling and text processing System.
\begin{itemize}
  \item Implemented a multi-thread crawler that automatically identify and extract online articles
  \item Processed articles with named entity recognition, keyword ranking, and category classification methods
  \item Developed a news feed system (http://www.kuaiwenbao.com)
\end{itemize}


\datedsubsection{\textbf{qRead Web Article Extraction}}{May 2014 -- May 2016}
\role{Java, PHP, JavaScript}{Research project}
A real-time article extractor using optimization method.
\begin{itemize}
  \item Designed a real-time article extraction algorithm to extract online articles
  \item Implemented article extraction RESTful APIs
  \item Set up a real-time article extraction system (http://www.http://kuaibianbao.com/english/index)
%  \item Assisted multiple text-related projects using qRead running in our research lab
\end{itemize}


%\datedsubsection{\textbf{Wocson Social Network Data Modeling}}{Dec. 2012 -- May 2014}
%\role{Java, JavaScript, jQuery, MongoDB, }{Research project}
%Wocson is a social network (weibo.com) data anlysis system using text modeling and machine learning methods.
%\begin{itemize}
%  \item Designed and developed web based applications for the social network big data modeling research
%  \item Demonstrated trends and sentiment analysis using data modeling and machine learning methods
%\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\faUsers\ Experience}
\datedsubsection{\textbf{MedVentive}}{June. 2012 -- Sept. 2012}
\role{SQL Developer Intern}{400 Fifth Ave., Suite 200 Waltham, MA 02451}
\begin{itemize}
  \item Created SQL scripts for custom measures based on HEDIS 2012 measures
  \item Implemented Batch files, and SQL scripts for patient’s data in quality rules engine.
  \item Migrated, merged and tested patients’ data and measures in quality rule engine
\end{itemize}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\faBook \ Publications}

\begin{itemize}
  \item qRead: A Fast and Accurate Article Extraction Method from Web Pages Using Partition Features Optimizations,
  \textit{\textbf{Jingwen Wang} and Jie Wang
  , 7th International Joint Conference Knowledge Discovery, Knowledge Engineering and Knowledge Management, Nov. 2015}
  \item KWB: An Automated Quick News System for Chinese Readers
  \textit{Bai, Yiqi and Yang, Wenjing and Zhang, Hao and \textbf{Wang, Jingwen} and Jia, Ming and Tong, Roland and Wang, Jie
  , ACL-IJCNLP 2015}
  \item Handling big data of online social networks on a small machine
  \textit{Jia, Ming and Xu, Hualiang and \textbf{Wang, Jingwen} and Bai, Yiqi and Liu, Benyuan and Wang, Jie
  , Computational Social Networks, 2015}
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\faHeartO\ Honors and Awards}

\datedline{\textit{College of Sciences Graduate Research Scholar Award}, Award by UMass Lowell}{2016}
\datedline{\textit{PM Raj Fund for Excellence in Computer Science}, Award by UMass Lowell}{2015}
\datedline{\textit{SIGMOD/PODS Travel Award}, Award by SIGMOD/PODS Conference}{May 2012}



\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
%  \item Blog: http://your.blog.me
  \item Linkedin: http://www.linkedin.com/in/jingwen-jessica-wang
  \item GitHub: https://github.com/jingwenjessica
  \item Languages: English - Fluent, Mandarin - Native speaker
\end{itemize}

%% Reference
\newpage
\bibliographystyle{IEEETran}
\bibliography{mycite}
\end{document}
